
% ====
\begin{rSection}{Experience}

{\bf NVIDIA Research, Austin, TX}         \hfill {\em July. 12 2021 -- } \\
11001 Lakeline Blvd \#100, Austin, TX, 78717 \\
Research Scientist \\
Lead research effort on AI semiconductor manufacturing, computational lithography, GPU/AI accelerated EDA. \\
\textbf{PhD Intern Mentorship}: Mingjie Liu (UT Austin, 2022), Zhengqi Gao (MIT, 2023), Guojin Chen (CUHK, 2024), Yun-Da Tsai (National Taiwan University, 2025), All result in impactful research projects with publication in top tier conferences.\\
\textbf{Service}: Topic Chair and Review Committee for NVIDIA Academic Research Grant, Technical Programme Committee (AAAI, DAC, NeurIPS) \\
\textbf{External Collaboration:} Arizona State University (Photonic Device and Photonic IC Design Automation), UT Austin (AI for Thermal Deisgn), TSMC, ASML (AI for Computational Lithography), National Taiwan University (LLM-Aided Chip Design)
	
{\bf Cadence Design Systems, San Jos\`{e}, CA}         \hfill {\em Mar. 22 2021 -- July. 9 2021 } \\
2655 Seely Ave, San Jose, CA 95134 \\
Lead Software Engineer \\
%Research and development on congestion aware placement algorithms. \\
%Project: 2.5D Padding for congestion-aware global placement.
	
{\bf The Chinese University of Hong Kong, N.T., Hong Kong}         \hfill {\em Sept. 14 2020 -- Mar. 1 2021} \\
Postdoctoral Fellow \\
%Research on machine learning algorithms for VLSI design manufacturability, parallel computing and adversarial machine learning. Publish on top conferences and journals. \\
%Project: Layout pattern generation, arithmetic logic detection, standard cell legalization 

{\bf Peking University, Beijing, China}         \hfill {\em July. 2019 -- Oct. 2019} \\
Research Intern

{\bf Cadence Design Systems, San Jos\'{e}, CA}         \hfill {\em July. 2018 -- Oct. 2018} \\
Software Engieering Intern
	
{\bf ASML Brion, San Jos\'{e}, CA}         \hfill {\em Sept. 2017 -- Dec. 2017} \\
Data Scientist Intern

%{\bf The Chinese University of Hong Kong, N.T., Hong Kong}         \hfill {\em Mar. 2016 -- June.~2016} \\
%Research Assistant

%{\bf Tianjin University, Tianjin, P.R.China}         \hfill {\em Sep. 2015 -- Jan. 2016} \\
%Teaching Assistant

\end{rSection}


