% !TeX spellcheck = en_US
\clearpage
\begin{rSection}{Publications}
%I have published 17 papers (10 first author) on prestigious journals and international conferences, 
%including 3 from IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{top journal in VLSI CAD}), 5 from ACM/IEEE Design Automation Conference (\textbf{top international conference in VLSI CAD, acceptance rate is around  20\%}), 2 from ACM/IEEE Asia and South Pacific Design Automation Conference (\textbf{acceptance rate is around 30\%}).
	
\iftrue

%\textbf{Conference Presentation as Speaker} [C3] [C5] [C8] [C9] [C10] [C13] [C18] \\
%\textbf{Best Paper Candidate} [C7]


\textbf{Book Chapters}
\begin{description}[font=\normalfont]
	
	\item[{[B1]}]{
		\textbf{Haoyu Yang}, Yibo Lin, Bei Yu,
		''Machine Learning for Mask Synthesis and Verification'', 
		in Machine Learning Applications in Electronic Design Automation,
		Springer, 2022.
	}
	
\end{description}


\textbf{Journal Papers}
\begin{description}[font=\normalfont]
	
\item[{[J17]}]{
	Xiaoxiao Liang, Yikang Ouyang, \textbf{Haoyu Yang}, Bei Yu, Yuzhe Ma,
	``RL-OPC: Mask Optimization with Deep Reinforcement Learning'', 
	accepted by IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}).
}
	
\item[{[J16]}]{
	Ziyi Wang, Zhuolun He, Chen Bai, \textbf{Haoyu Yang}, Bei Yu,
	``Efficient Arithmetic Block Identification with Graph Learning and Network-flow'', 
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 42, no. 08, pp. 2591–2603, 2023.
}	


\item[{[J15]}]{
	\textbf{Haoyu Yang}, Shuhe Li, Wen Chen, Piyush Pathak, Frank Gennari, Ya-Chieh Lai and Bei Yu, ``DeePattern: Layout Pattern Generation with Transforming Convolutional Auto-Encoder'',
	IEEE Transactions on Semiconductor Manufacturing (\textbf{TSM}), vol. 35, no. 1, pp. 67–77, 2022. (\textcolor{red}{Best Paper Award})
}

\item[{[J14]}]{
	Guojin Chen, Wanli Chen, Qi Sun, Yuzhe Ma, \textbf{Haoyu Yang}, Bei Yu,
	``DAMO: Deep Agile Mask Optimization for Full Chip Scale'', 
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 9, pp. 3118–3131, 2022.
}

\item[{[J13]}]{
	Hao Geng, \textbf{Haoyu Yang}, Lu Zhang, Jin Miao, Fan Yang, Xuan Zeng, Bei Yu,
	``Hotspot Detection via Attention-based Deep Layout Metric Learning'', 
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 8, pp. 2685–2698, 2022.
}
	
\item[{[J12]}]{
	Wei Zhong, Shuxiang Hu, Yuzhe Ma, \textbf{Haoyu Yang}, Xiuyuan Ma, Bei Yu,
	``Deep Learning-Driven Simultaneous Layout Decomposition and Mask Optimization'', 
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 3, pp. 709–722, 2022.
}


\item[{[J11]}]{
	Guyue Huang, Jingbo Hu, Yifan He, Jialong Liu, Mingyuan Ma, Zhaoyang Shen, Juejian Wu, Yuanfan Xu, Hengrui Zhang, Kai Zhong, Xuefei Ning, Yuzhe Ma, \textbf{Haoyu Yang}, Bei Yu, Huazhong Yang, Yu Wang,
	``Machine Learning for Electronic Design Automation: A Survey'', 
	ACM Transactions on Design Automation of Electronic Systems (\textbf{TODAES}), vol. 25, no. 5, 2021.
}
	
\item[{[J10]}]{
	\textbf{Haoyu Yang}, Wei Zhong, Yuzhe Ma, Hao Geng, Ran Chen, Wanli Chen, Bei Yu,
	``VLSI Mask Optimization: From Shallow To Deep Learning'', 
	Integration, the VLSI Journal, vol. 77, Mar., pp. 96–103, 2021.
}

\item[{[J9]}]{
	Haocheng Li, Satwik Patnaik, Abhrajit Sengupta, \textbf{Haoyu Yang}, Johann Knechtel, Bei Yu, Evangeline F.Y. Young, Ozgur Sinanoglu, 
	``Deep Learning Analysis for Split Manufactured Layouts with Routing Perturbation'',  
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 40, no. 10, pp. 1995–2008, 2021.
}
	
\item[{[J8]}]{
	Ran Chen, Wei Zhong, \textbf{Haoyu Yang}, Hao Geng, Xuan Zeng, Bei Yu, ``Faster Region-based Hotspot Detection'',  
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 3, pp. 669–680, 2022. 
}
	
\item[{[J7]}]{
	\textbf{Haoyu Yang}, Shuhe Li, Cyrus Tabery, Bingqing Lin and Bei Yu, ``Bridging the Gap Between Layout Pattern Sampling and Hotspot Detection via Batch Active Learning'', IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}),  vol. 40, no. 7, pp. 1464–1475, 2021.
}	

\item[{[J6]}]{
	Kang Liu, \textbf{Haoyu Yang}, Yuzhe Ma, Benjamin Tan, Bei Yu, Evangeline F. Y. Young, Ramesh Karri, Siddharth Garg, ''Are Adversarial Perturbations a Showstopper for ML-Based CAD? A Case Study on CNN-Based Lithographic Hotspot Detection'', ACM Transactions on Design Automation of Electronic Systems (\textbf{TODAES}), vol.~25, no.~5, 2020.
}	
	
\item[{[J5]}]{
	Hao Geng, Wei Zhong, \textbf{Haoyu Yang}, Yuzhe Ma, Joydeep Mitra and Bei Yu, ''SRAF Insertion via Supervised Dictionary Learning'', IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol.~39, no.~10, pp.~2849-2859, 2020.
}	
	
\item[{[J4]}]{
	\textbf{Haoyu Yang}, Shuhe Li, Zihao Deng, Yuzhe Ma, Bei Yu and Evangeline F. Y. Young, ''GAN-OPC: Mask Optimization with Lithography-guided Generative Adversarial Nets'', IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol.~39, no.~10, pp.~2822-2834, 2020.
}

\item[{[J3]}]{
	\textbf{Haoyu Yang}, Jing Su, Yi Zou, Yuzhe Ma, Bei Yu, Evangeline F.~Y.~Young, ``Layout Hotspot Detection with Feature Tensor Generation and Deep Biased Learning'', IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol.~38, no.~6, pp.~1175-1187, 2019.
}
	
\item[{[J2]}]{
	\textbf{Haoyu Yang}, Luyang Luo, Jing Su, Chenxi Lin and Bei Yu, ``Imbalance Aware Lithography Hotspot Detection: A Deep Learning Approach'', Journal of Micro/Nanolithography, MEMS, and MOEMS (JM3), 16(3), 033504, 2017.
}

\item[{[J1]}]{
    Zaifeng Shi, \textbf{Haoyu Yang}, Wenxiang Cong and Ge Wang,
    ``An Edge-on Charge-transfer Design for Energy-resolved X-ray Detection'',
    Physics in Medicine and Biology, 61(11):4183-4200, 2016.
}

\end{description}

\textbf{Conference Papers}
\begin{description}[font=\normalfont]
	
	\item[{[C31]}] Tao Zhang, \textbf{Haoyu Yang}, Kang Liu, Zhiyao Xie, ``APPLE: An Explainer of ML Predictions on Circuit Layout at the Circuit-Element Level'', IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Incheon, Jan 22-25, 2024.
	
	
	
	\item[{[C30]}] Su Zheng, \textbf{Haoyu Yang}, Binwu Zhu, Bei Yu, Martin D.F. Wong, ``LithoBench: Benchmarking AI Computational Lithography for Semiconductor Manufacturing'', Neural Information Processing Systems (\textbf{NeurIPS}), New Orleans, Dec. 10–16, 2023.
	
		
	\item[{[C29]}] Mingjie Liu, \textbf{Haoyu Yang}, Brucek Khailany, Haoxing Ren, ``An Adversarial Active Sampling-based Data Augmentation Framework for AI-Assisted Lithography Modeling'', IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), San Francisco, CA, Oct 29- Nov 2, 2023.
	
	\item[{[C28]}] Guojin Chen, Zehua Pei, \textbf{Haoyu Yang}, Yuzhe Ma, Bei Yu, Martin Wong, ``Physics-Informed Optical Kernel Regression Using Complex-valued Neural Fields'', ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, July 09-13, 2023.
	
		
	\item[{[C27]}] Guojin Chen, \textbf{Haoyu Yang}, Bei Yu, ``GPU Accelerated Matrix Cover Algorithm for Multiple Patterning Layout Decomposition'', SPIE Intl. Symp. Advanced Lithography Conference, San Jose, Feb. 26–Mar. 02, 2023.

	\item[{[C26]}] \textbf{Haoyu Yang}, Haoxing Ren, ``Enabling Scalable AI Computational Lithography with Physics-Inspired Models'', IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Tokyo, Jan 16-19, 2023.
	
	\item[{[C25]}] Mingjie Liu, \textbf{Haoyu Yang}, Zongyi Li, Kumara Sastry, Saumyadip Mukhopadhyay, Selim Dogru, Anima Anandkumar, David Pan, Brucek Khailany, Haoxing Ren,
	``An Adversarial Active Sampling-based Data Augmentation Framework for Manufacturable Chip Design'',
	Neural Information Processing Systems ML for Systems Workshop, New Orleans, LA, Dec 3, 2022.
	
	\item[{[C24]}] \textbf{Haoyu Yang}, Zongyi Li, Kumara Sastry, Saumyadip Mukhopadhyay, Mark Kilgard, Anima Anandkumar, Brucek Khailany, Vivek Singh, Haoxing Ren,
	``Generic Lithography Modeling with Dual-band Optics-Inspired Neural Networks'',
	ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, June 10–14, 2022.
	
	\item[{[C23]}] \textbf{Haoyu Yang}, Kit Fung, Yuxuan Zhao, Yibo Lin, Bei Yu,
	``Mixed-Cell-Height Legalization on CPU-GPU Heterogeneous Systems'',
	IEEE/ACM Proceedings Design, Automation and Test in Europe (\textbf{DATE}), Antwerp, Belgium, Mar 16–23, 2022.
	
	\item[{[C22]}] Zhuolun He, Ziyi Wang, Chen Bai, \textbf{Haoyu Yang}, Bei Yu, ``Graph Learning-Based Arithmetic Block Identification'',
	IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Munich, Germany, Nov 1–4, 2021.
	
	\item[{[C21]}] Xiaopeng Zhang, \textbf{Haoyu Yang}, Evangeline F.Y. Young, ``Attentional Transfer is All You Need: Technology-aware Layout Pattern Generation'',
	ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, Dec 5–9, 2021.
	
	
	\item[{[C20]}] Yifeng Xiao, Miaodi Su, \textbf{Haoyu Yang}, Jianli Chen, Jun Yu, Bei Yu,
	``Low-Cost Lithography Hotspot Detection with Active Entropy Sampling and Model Calibration'',
	ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, Dec 5–9, 2021.
	
	\item[{[C19]}] Wei Li, Guojin Chen, \textbf{Haoyu Yang}, Ran Chen, Bei Yu,
	``Learning Point Clouds in EDA'', ACM International Symposium on Physical Design (\textbf{ISPD}), Mar. 21-24, 2021.

	\item[{[C18]}] \textbf{Haoyu Yang}, Shifan Zhang, Kang Liu, Siting Liu, Benjamin Tan, Ramesh Karri, Siddharth Garg, Bei Yu, Evangeline F.Y. Young,
	``Attacking a CNN-based Layout Hotspot Detector Using Group Gradient Method'', 
	IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Tokyo, Jan. 18–21, 2021.

    \item[{[C17]}] Hao Geng, \textbf{Haoyu Yang}, Lu Zhang, Jin Miao, Fan Yang, Xuan Zeng, Bei Yu, 
    ``Hotspot Detection via Attention-based Deep Layout Metric Learning'', 
    IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Nov. 2–5, 2020.
    
    \item[{[C16]}] Guojin Chen, Wanli Chen, Yuzhe Ma, \textbf{Haoyu Yang}, Bei Yu,
     ``DAMO: Deep Agile Mask Optimization for Full Chip Scale'', 
     IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Nov. 2–5, 2020.
	
	\item[{[C15]}] Wei Zhong, Shuxiang Hu, Yuzhe Ma, \textbf{Haoyu Yang}, Xiuyuan Ma, Bei Yu, 
	``Deep Learning-Driven Simultaneous Layout Decomposition and Mask Optimization'', 
	ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, July 19–23, 2020.
	
	\item[{[C14]}] \textbf{Haoyu Yang}, Wen Chen, Piyush Pathak, Frank Gennari, Ya-Chieh Lai, Bei Yu, 
	``Automatic Layout Generation with Applications in Machine Learning Engine Evaluation'', 
	ACM/IEEE Workshop on Machine Learning for CAD (MLCAD), Alberta, Canada, Sep. 3–4, 2019.
	
	
	\item[{[C13]}] \textbf{Haoyu Yang}, Wei Zhong, Yuzhe Ma, Hao Geng, Ran Chen, Wanli Chen, Bei Yu,
	 ``VLSI Mask Optimization: From Shallow To Deep Learning'', 
	 IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Beijing, Jan. 13–16, 2020.

	\item[{[C12]}]{
	Haocheng Li, Satwik Patnaik, Abhrajit Sengupta, \textbf{Haoyu Yang}, Johann Knechtel, Bei Yu, Evangeline F.Y. Young, Ozgur Sinanoglu, 
	``Attacking Split Manufacturing From a Deep Learning Perspective'',  
	ACM/IEEE Design Automation Conference (\textbf{DAC}), Las Vegas, NV, June 2--6, 2019.
	}
	\item[{[C11]}]{
	Ran Chen, Wei Zhong, \textbf{Haoyu Yang}, Hao Geng, Xuan Zeng, Bei Yu, ``Faster Region-based Hotspot Detection'',  
	ACM/IEEE Design Automation Conference (\textbf{DAC}), Las Vegas, NV, June 2--6, 2019.
	}
	\item[{[C10]}]{
	\textbf{Haoyu Yang}, Piyush Pathak, Frank Gennari, Ya-Chieh Lai and Bei Yu, ``DeePattern: Layout Pattern Generation with Transforming Convolutional Auto-Encoder'',  
	ACM/IEEE Design Automation Conference (\textbf{DAC}), Las Vegas, NV, June 2--6, 2019.
	}
	\item[{[C9]}]{
	\textbf{Haoyu Yang}, Piyush Pathak, Frank Gennari, Ya-Chieh Lai and Bei Yu, ``Hotspot Detection Using Squish-net'',  
	SPIE Intl. Symp. Advanced Lithography Conference, San Jose, CA, Feb. 24--28, 2019.
	}
	\item[{[C8]}]{
	\textbf{Haoyu Yang}, Piyush Pathak, Frank Gennari, Ya-Chieh Lai and Bei Yu, ``Detecting Multi-Layer Layout Hotspots with Adaptive Squish Patterns'',  
	IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Tokyo, Jan. 21--24, 2019.
	}
	\item[{[C7]}]{
	Hao Geng, \textbf{Haoyu Yang}, Yuzhe Ma, Joydeep Mitra and Bei Yu, ``SRAF Insertion via Supervised Dictionary Learning'',  
	IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Tokyo, Jan. 21--24, 2019. (\textcolor{red}{Best Paper Award Candidate})
	}
	\item[{[C6]}]{
		Hao Geng, \textbf{Haoyu Yang}, Xuan Zeng and Bei Yu, ``Sparse VLSI Layout Feature Extraction: A Dictionary Learning Approach'',  
		IEEE Computer Society Annual Symposium on VLSI, Hong Kong, China, July 9--11, 2018.
	}
	\item[{[C5]}]{
		\textbf{Haoyu Yang}, Shuhe Li, Yuzhe Ma, Bei Yu and Evangeline F.~Y.~Young, ``GAN-OPC: Mask Optimization with Lithography-guided Generative Adversarial Nets'', ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, June 24--28, 2018. 
	}	
	\item[{[C4]}]{
		\textbf{Haoyu Yang}, Yajun Lin, Bei Yu, Evangeline F.~Y.~Young
		``Lithography Hotspot Detection: From Shallow to Deep Learning'',
		IEEE International System-on-Chip Conference (SOCC), Munich, Germany, September 5--8, 2017. 
	}
	\item[{[C3]}]{
		\textbf{Haoyu Yang}, Jing Su, Yi Zou, Bei Yu, Evangeline F.~Y.~Young
		``Layout Hotspot Detection with Feature Tensor Generation and Deep Biased Learning'',
		ACM/IEEE Design Automation Conference (\textbf{DAC}), Austin, TX, Jun. 18--Jun. 22, 2017. 
	}
	\item[{[C2]}]{
		\textbf{Haoyu Yang}, Luyang Luo, Jing Su, Chenxi Lin, Bei Yu,
		``Imbalance Aware Lithography Hotspot Detection: A Deep Learning Approach'',
		SPIE Intl. Symp. Advanced Lithography Conference, San Jose, CA, Feb. 26--Mar. 2, 2017. 
	}
	\item[{[C1]}]{
		Hang Zhang, \textbf{Haoyu Yang}, Bei Yu and Evangeline F. Y. Young,
		``VLSI Layout Hotspot Detection Based on Discriminative Feature Extraction'',
		IEEE Asia Pacific Conference on Circuits \& Systems, Jeju, Korea, Oct. 25--28, 2016.
	}
\end{description}


%\textbf{Dissertation}
%\begin{description}[font=\normalfont]
%\item[{[Ph.D.]}]{
%	Haoyu Yang,
%	``Intelligent VLSI Design for Manufacturability'',
%	Chinese University of Hong Kong, June 2020.
%}

%\item[{[B.Eng.]}]{
   % Haoyu Yang,
    %``Modeling and Simulating of Network on Chip'',
    %Tianjin University, July 2015.
    %(\textbf{Excellent Dissertation Award})
%}
%\end{description}
\fi




\end{rSection}

